---
title: "MDP"
author: "Melissa Wong"
date: "November 21, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
rm(list = ls())

knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(MDPtoolbox)

source("data_prep.R")
source("helper_calcs.R")
source("get_stationary_distribution.R")

filter_raw_data()

load("../CleanData/filtered_sentiment_data.Rdata")
load("../CleanData/filtered_product_lists.Rdata")
load("../CleanData/filtered_survey_data.Rdata")
```

# NPS

## States 

\begin{itemize}
  \item Very High: $NPS > 60.0$
  \item Moderately High: $60.0 \ge NPS > 45.0$
  \item Normal: $45.0 \ge NPS > 35.0$
  \item Moderately Low: $35.0 \ge NPS > 8.0$
  \item Very Low: $8.0 \ge NPS$
\end{itemize}


## Actions

\begin{table}[h!]
\begin{tabular}{lc|c|c|c|c|c|}
\cline{3-7}
\multicolumn{1}{c}{}     &                & \multicolumn{5}{c|}{Applicable NPS States}                                                                                                            \\ \hline
\multicolumn{1}{|c|}{ID} & Action         & Very Low & \begin{tabular}[c]{@{}c@{}}Moderately\\ Low\end{tabular} & Normal & \begin{tabular}[c]{@{}c@{}}Moderately \\ High\end{tabular} & Very High \\ \hline
\multicolumn{1}{|l|}{1}  & Do Nothing     & Y        & Y                                                        & Y      & Y                                                          & Y         \\ \hline
\multicolumn{1}{|l|}{2}  & Software Patch & Y        & Y                                                        & Y      & Y                                                          & Y         \\ \hline
\multicolumn{1}{|l|}{3}  & TBD            & Y        & Y                                                        & Y      & Y                                                          & Y         \\ \hline
\end{tabular}
\end{table}

## Transition Matrices

### Action: Do Nothing
```{r warning=FALSE}
# Define NPS states
NPS_VERY_HIGH <- 60.0
NPS_MOD_HIGH <- 45.0
NPS_NORMAL <- 35.0
NPS_MOD_LOW <- 8.0

res <- survey.consumer.all %>%
  group_by(SeriesName,
           time = floor_date(as.Date(Date.Survey, format = "%m/%d/%y"), unit = "month")) %>% 
  NPSTransitions(NPS_VERY_HIGH, NPS_MOD_HIGH, NPS_NORMAL, NPS_MOD_LOW)

PConsumer_A1 <- res$P

knitr::kable(PConsumer_A1, row.names=TRUE, caption = "Consumer, Do Nothing")

```


```{r warning=FALSE}
# Define NPS states
NPS_VERY_HIGH <- 60.0
NPS_MOD_HIGH <- 45.0
NPS_NORMAL <- 35.0
NPS_MOD_LOW <- 8.0

res <- survey.comm.all %>%
  group_by(SeriesName,
           time = floor_date(as.Date(Date.Survey, format = "%m/%d/%y"), unit = "month")) %>% 
  NPSTransitions(NPS_VERY_HIGH, NPS_MOD_HIGH, NPS_NORMAL, NPS_MOD_LOW)

PComm_A1 <- res$P

knitr::kable(PComm_A1, row.names=TRUE, caption = "Commercial, Do Nothing")

```

### Action: Software Patch

Assume that a software patch reduces the probability of transitioning to Very_Low by $p\%$ as compared to Do Nothing, and that percentage is evenly distributed among the remaining 4 states.  Set $p=10\%$ for illustration.

```{r}
p <- 0.1
n <- nrow(PConsumer_A1)
delta <- p * PConsumer_A1$VERY_LOW

PConsumer_A2 <- PConsumer_A1
PConsumer_A2$VERY_LOW <- PConsumer_A2$VERY_LOW - delta
PConsumer_A2$MOD_LOW <- PConsumer_A2$MOD_LOW + delta/(n-1)
PConsumer_A2$NORMAL <- PConsumer_A2$NORMAL + delta/(n-1)
PConsumer_A2$MOD_HIGH <- PConsumer_A2$MOD_HIGH + delta/(n-1)
PConsumer_A2$VERY_HIGH <- PConsumer_A2$VERY_HIGH + delta/(n-1)

knitr::kable(PConsumer_A2, row.names=TRUE, caption = "Consumer, Software Patch")

```

```{r}
p <- 0.1
n <- nrow(PComm_A1)
delta <- p * PComm_A1$VERY_LOW

PComm_A2 <- PComm_A1
PComm_A2$VERY_LOW <- PComm_A2$VERY_LOW - delta
PComm_A2$MOD_LOW <- PComm_A2$MOD_LOW + delta/(n-1)
PComm_A2$NORMAL <- PComm_A2$NORMAL + delta/(n-1)
PComm_A2$MOD_HIGH <- PComm_A2$MOD_HIGH + delta/(n-1)
PComm_A2$VERY_HIGH <- PComm_A2$VERY_HIGH + delta/(n-1)

knitr::kable(PComm_A2, row.names=TRUE, caption = "Commercial, Software Patch")

```

## Rewards

Assume Rewards are the same for commercial and consumer segments and assume reward matrix is of the form shown below with a parameter $r$.

\begin{table}[h!]
\begin{tabular}{l|c|c|c|c|c|}
\cline{2-6}
\multicolumn{1}{c|}{}                                                           & Very Low & \begin{tabular}[c]{@{}c@{}}Moderately\\ Low\end{tabular} & Normal & \begin{tabular}[c]{@{}c@{}}Moderately \\ High\end{tabular} & Very High \\ \hline
\multicolumn{1}{|l|}{Very Low}                                                  & -2r      & -r                                                       & 0      & r                                                          & 2r        \\ \hline
\multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}Moderately\\ Low\end{tabular}}  & -2r      & -r                                                       & 0      & r                                                          & 2r        \\ \hline
\multicolumn{1}{|l|}{Normal}                                                    & -2r      & -r                                                       & 0      & r                                                          & 2r        \\ \hline
\multicolumn{1}{|c|}{\begin{tabular}[c]{@{}c@{}}Moderately\\ High\end{tabular}} & -2r      & -r                                                       & 0      & r                                                          & 2r        \\ \hline
\multicolumn{1}{|c|}{Very High}                                                 & -2r      & -r                                                       & 0      & r                                                          & 2r        \\ \hline
\end{tabular}
\end{table}

Set $r=10$ for illustration purposes.

### Action: Do Nothing

```{r}
val <- 10
R_A1 <- matrix(rep(c(-2*val, -1*val, 0, val, 2*val),n),
               nrow=n,
               byrow=TRUE)

knitr::kable(R_A1, caption = "Rewards, Do Nothing")
```

### Action: Software Patch

Assume there is a cost, $c$, with deploying a software patch.  Set $c = 5$ for illustration purposes.

```{r}
c <- 5
R_A2 <- R_A1 - c

knitr::kable(R_A2, caption = "Rewards, Software Patch")
```


## MDP Consumer

```{r}

# Transitions
P1 <- as.matrix(PConsumer_A1[2:6])
P2 <- as.matrix(PConsumer_A2[2:6])
P <- array(c(P1, P2), dim=c(dim(P1), 2))

# Rewards
R <- array(c(R_A1, R_A2), dim=c(dim(P1), 2))

# Check validity
mdp_check(P, R)


# Discount factor
discount <- 0.95 
```

```{r}
# Objective is to maximize rewards
#Policy Iteration
mdp_policy_iteration(P, R, discount)
```

```{r}
# Objective is to maximize rewards
# Linear Programming
mdp_LP(P, R, discount)
```

```{r}
# Stationary Distributions
get_stationary_distribution(P1)

get_stationary_distribution(P2)
```

## MDP Commercial

```{r}

# Transitions
P1 <- as.matrix(PComm_A1[2:6])
P2 <- as.matrix(PComm_A2[2:6])
P <- array(c(P1, P2), dim=c(dim(P1), 2))

# Rewards
R <- array(c(R_A1, R_A2), dim=c(dim(P1), 2))

# Check validity
mdp_check(P, R)


# Discount factor
discount <- 0.95 
```


```{r}
# Objective is to maximize rewards
#Policy Iteration
mdp_policy_iteration(P, R, discount)
```

```{r}
# Objective is to maximize rewards
# Linear Programming
mdp_LP(P, R, discount)
```


```{r}
# Stationary Distributions
get_stationary_distribution(P1)

get_stationary_distribution(P2)
```